### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence elationship is not etemined between two transactions by Def 6. 1-If $T_i$ and $T_j$ are two transactions both committed with commit instant of $T_j$ being greater than commit instant of $T_i$ then $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$. 2-If two operation belong to the same transaction, then the one that occurs earlier in natural order of transaction precedes the other. 3- If $T_i$ is committed and $T_j$ is not, $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$. 4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ or it is $op_i \rightarrow op_j$. 5- Otherwise, it means some operations in $T_i$ precede some of thos in $T_j$ and the other way around, for thos pairs not having such relationship it is assigned arbitrarily.\\

Def 9- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if there is a precedence relationship between $op_{T_i}$ and $op_{T_i}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\

>>>>

Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence relationship is not detemined between two operations by Def 6. 1-If $T_i$ and $T_j$ are two transactions both committed with commit instant of $T_j$ being greater than commit instant of $T_i$ then $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$. 2-If two operation belong to the same transaction, then the one that occurs earlier in natural order of transaction precedes the other. 3- If $T_i$ is committed and $T_j$ is not, $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$. 4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ OR it is $op_i \rightarrow op_j$. 5- Otherwise, it means some operations in $T_i$ precede some of thos in $T_j$ and the other way around, for thos pairs not having such relationship it is assigned arbitrarily.\\

Def 9- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\

Def 10- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established.\\

Corrolary: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}

proof: Follows imeediately from Def 9 and Def 10.
